---
title: "FA-7 | APM1110"
author: "LEIANA MARI D. AQUINO"
date: "2023-04-19"
output: 
  html_notebook
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

EXERCISES 5.1
Use R to solve the following.

## The Memory Stick

A machine produces memory sticks of varying lengths, distributed uniformly between 2 and 12 mm. Memory sticks longer than 10 mm do not meet the design criterion, and must be scrapped.

(a) Calculate the probability that a memory stick will be scrapped.
```
Let X denote the length of the memory sticks. It follows a uniform distribution of (2, 12). 
```
The pdf of a uniform distribution is given by

$$
\begin{equation}
f(x) = 
\begin{cases} 
\ \frac{1}{12-2}, &  2 \le x \le 12 \\
0,         & \text{otherwise }
\end{cases}
\end{equation}
$$
```
If the memory sticks longer than 10mm will be scrapped.
```
We will have $P(x > 10)$. Now, for $2 \le a \le 12$,
$$
P(x>a)=\int_a^{12} f(x) =\int_a^{12} \frac{1}{10}dx=\frac{1}{10}[x]_a^{12}
$$
Putting $a=10$,
$$
P(x>10)=\frac{12-10}{10}=\frac{2}{10}=0.2
$$
```
The probability that a memory stick will be scrapped is 0.2
```
Using R,
```{r, echo=FALSE}
curve(dunif(x, 2, 12), xlim = c(0, 10))
curve(punif(x, 2, 12), xlim = c(0, 10))
```

(b) Simulate 50 memory stick lengths and obtain a histogram of the simulated values. Calculate the simulated mean and variance.

To simulate 50 memory sticks, write `x = runif(50, 2, 12)`.

Then, we can use the round function to convert the decimal values into 0s or 1s. `round(x, 2)`

To see what they are, we have
```{r, echo=FALSE}
 x = runif(50, 2, 12)
 round(x, 2)
```

To obtain the empirical mean, write `mean(x)`
```{r, echo=FALSE}
mean(x);
```

and variance, write `var(x)`
```{r, echo=FALSE}
var(x);
```

Its histogram, write `hist(x)`
```{r, echo=FALSE}
  hist(x)  # frequency histogram
  rug(x)   # small tick marks show location of each simulated value
```

## Electronic engineering laboratory
Students in an electronic engineering laboratory measure current in using an ammeter. Due to several random factors, the measurement X follows the pdf $f(x)=0.025x + b, 2 < x <6$

(a) Show that, for this to be a genuine probability density, $b = 0.15$.
Since f(x) is pdf so following must be true, we'll have this equation (1):
$$
\int_2^{6} f(x)dx =1
$$
Now, the equation (2)
$$
\int_2^{6} [0.025x + b]dx = [\frac{0.025x^2}{2}+bx]_2^6=0.4 + 4b
$$
Equating equation (1) and (2), we have
$$
0.4 + 4b = 1\\
4b=0.6 \\
b=0.15
$$
Now, we solve it using R with this code:
```
lower = 2
upper = 6
b <- 0.15
f <- function(x) ifelse(6 > x & x > 2, 0.025*x + b, 0)
pdf <- integrate(f, lower = 2, upper = 6)$val
y <- 0.1
gp <- (abs(PDensity - 1) < y) 
gp
```
We'll have `TRUE` to denote that b = 0.15 is a genuine probability
```{r, echo=FALSE}
lower = 2
upper = 6
b <- 0.15
f <- function(x) ifelse(6 > x & x > 2, 0.025*x + b, 0)
pdf <- integrate(f, lower = 2, upper = 6)$val
y <- 0.1
gp <- (abs(pdf - 1) < y) 
gp
```


(b) Find the probability that the measurement of the current exceeds 3.
$$
P(X>3)= \int_3^6 [0.025x + 0.15]dx=[\frac{0.025x^2}{2}+0.15x]_3^6=0.7875
$$
Now, we solve it using R with this code: `e_3 <- integrate(f, lower = 3, upper = 6)$val`
```{r, echo=FALSE}
lower = 2
upper = 6

e_3 <- integrate(f, lower = 3, upper = 6)$val
cat("Probability that measurement exceeds 3 is =", e_3)
```


(c) Find $E(X)$
$$
E(X)=\int_2^6[0.025x + 0.15]dx=[\frac{0.025x^3}{2}+\frac{0.15x^2}{2}]_3^6=4.133
$$

Now, we solve it using R with this code: `eX <- integrate(function(x) x * f(x), lower = 2, upper = 6)$val`

```{r, echo=FALSE}
lower = 2
upper = 6

eX <- integrate(function(x) x * f(x), lower = 2, upper =6)$val
cat("Expected value of X =", round(eX, 2))
```


## Radio Communications System

In a radio communications system, the phase difference X between the transmitter and receiver is modeled as having a uniform density in $[-\pi,\pi]$. Find $P(X \le0)$ and $P(X \le \pi/2)$.

The pdf of a uniform distribution is given by

$$
\begin{equation}
f(\theta) = 
\begin{cases} 
\ \frac{1}{2\pi}, &  -\pi \le \theta \le \pi \\
0,         & \text{otherwise }
\end{cases}
\end{equation}
$$

```{r, echo=FALSE}
lower = 0
upper = 3.14/2

lowerInterval <- c(-3.14)
upperInterval <- c(3.14)

pdf <- function(x) {
  ifelse(abs(x) <= 3.14, 1/(2*3.14), 0)
}
```

Hence, $P(X \le 0)$:
```{r, echo=FALSE}
probability_1 <- integrate(pdf, lower = lowerInterval, upper = 0)$val
probability_1
```

For $P(X \le \pi/2)$:
```{r, echo=FALSE}
probability_2 <- integrate(pdf, lower = lowerInterval, upper = 3.14/2)$val
probability_2
```

The code for these are:
```
lower = 0
upper = 3.14/2

lowerInterval <- c(-3.14)
upperInterval <- c(3.14)

pdf <- function(x) {
  ifelse(abs(x) <= 3.14, 1/(2*3.14), 0)
}
probability_1 <- integrate(pdf, lower = lowerInterval, upper = 0)$val
probability_1

probability_2 <- integrate(pdf, lower = lowerInterval, upper = 3.14/2)$val
probability_2
```